CONEM2024-0025\\ NEW ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO ATTRIBUTE WEIGHTS AND FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX

### 2024-03-14 accepted/CONEM2024/FCPCOM/CONEM2024.tex
In the middle of the stones flowers are born

	\section{CONCLUSIONS AND FURTHER WORK}

    In this article we present a new methodology for multicriteria ABC classification as an analytical hierarchy process which includes a procedure to force the consitences of the pairwise comparison matrices, as well as a procedure for assigning weights to the products evaluated according to qualitative criteria and a new equation for calculating the weights of the products in the multicriteria classification. This methodology was tested using data provided by three companies, from three different sectors. As a result, we verified the importance and efficiency of the method developed to force the consistency of the Matrix. We also verified that the new methodology proposed for multicriteria ABC classification generated very coherent results, giving the appropriate importance to the products, according to all the evaluated criteria.

The methodologies developed and results found will be used as a basis for building a portfolio with the identification of product demand pattern and, subsequently, for the development of a combined methodology for demand forecasting. These will be the next works that we will be developing.

    \section{AGRADECIMENTOS}

>>>>

	\section{CONCLUSIONS AND FURTHER WORKS}

    In this article we present a new methodology for multicriteria ABC classification with Analytical Hierarchy Process which includes a procedure to force the consitences of the pairwise comparisons matrices, as well as a procedure for assigning weights to the products evaluated according to qualitative criteria and a new equation for calculating the weights of the products in the multicriteria classification. This methodology was tested using data provided by three companies, from three different sectors. As a result, we verified the importance and efficiency of the method developed to force the matrices consistency. We also verified that the new methodology proposed for multicriteria ABC classification generated very coherent results, giving the appropriate importance to the products, according to all the evaluated criteria.

As further works, the methodologies developed and results found will be used as a basis for building a portfolio with the identification of product demand patterns and, subsequently, for the development of a combined methodology for demand forecasting of small companies.

    \section{ACKNOWLEDGEMENTS}

Huge thanks to the teams responsible for developing elementary OS, as well as yandex translator, grammarly, duckduckgo, gummi, CodeBlocks, git, GitHub, gcc, and TeXLive libraries. Without the availability of these tools, the 'COPSolver's library for solving the multicriteria classification problem' could never have been developed. I am also very grateful to my co-workers Regilda da Costa e Silva Menêzes and Marcos Luiz Henrique for their constant support to the projects I develop and to my dear advisees , among others, for having participated so enthusiastically in the projects that gave rise to this software, in particular for having made the effort to describe real processes in such detail. I would also like to thank the company in the plastic bag sector and other companies that made the studies possible as well as the identification of the new optimization problem addressed in COPSolver\_1.0-1. \\
